### 2021-04-21 paper/ase21/eval.tex
[ASE21] Minor typo in eval

We evaluate $\tool$ using the following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detected by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effectiveness of Refinement)} Does the condition-based refinement
    improve the analysis precision with modest performance overhead?
  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
    specification bugs in the latest version of ECMAScript?
\end{itemize}
Because the draft of the next ECMAScript (ES12, 2021) is fixed on March 9,
2021, we analyzed all 864 versions in the official
ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the last
three years from January 1, 2018 to March 9, 2021.  We performed our experiments
on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7 and 32GB of
RAM.

@@

We measured the analysis precision with the number of true bugs in
the type-related specification bugs detected by $\tool$.
As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is \inred{52.0}\%; \inred{92} out of \inred{177} detected bugs are true bugs.
The reference checker detected the most bugs with \inred{62.2}\% precision;
\inred{17} unknown variables (\stextsf{UnknownVar}) and
\inred{44} deplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
We found \inred{4} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
\inred{5} assertion failures (\stextsf{Assertion}) with \inred{16.1}\% precision.
Finally, the operand checker detected
\inred{2} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
\inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.

>>>>

We evaluate $\tool$ using the following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detected by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effectiveness of Refinement)} Does the condition-based refinement
    improve the analysis precision with modest performance overhead?
  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
    specification bugs in the latest version of ECMAScript?
\end{itemize}
Because the draft of the next ECMAScript (ES12, 2021) is fixed on March 9,
2021, we analyzed all 864 versions in the official
ECMAScript repository\footnote{https://github.com/tc39/ecma262} for the last
three years from January 1, 2018 to March 9, 2021.  We performed our experiments
on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7 and 32GB of
RAM.

@@

We measured the analysis precision with the number of true bugs in
the type-related specification bugs detected by $\tool$.
As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is \inred{52.0}\%; \inred{92} out of \inred{177} detected bugs are true bugs.
The reference checker detected the most bugs with \inred{62.2}\% precision;
\inred{17} unknown variables (\stextsf{UnknownVar}) and
\inred{44} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
We found \inred{4} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
\inred{5} assertion failures (\stextsf{Assertion}) with \inred{16.1}\% precision.
Finally, the operand checker detected
\inred{2} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
\inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.
